He-Man: A domain-specific language for lightweight concurrency

### 2012-03-06 paper/paper.tex
Fix the grammars a bit.
Some tweaks and whatnot.

The underlying abstract syntax for the front-end He-Man language is a
fairly conventional imperative, statement-based, first-order language,
shown in Figure \ref{fig:front-syntax}. The notable constructs are
\b{Spawn}, creating a new thread, which takes a list of arguments
and launches the associated code with those arguments available to it,
and \b{Wait}, which takes an event expression as an argument and
blocks until the event has ``completed''. Note that \b{Call} is for
calling foreign functions; He-Man does not have its own notion of
function.

@@

\begin{figure}[ht]
\centering
\bnf{
\i{Stmt}
\p{\b{Decl} (\i{Var}, \i{Type}) \i{Expr}}
\a{\b{While} \i{Expr} [\i{Stmt}]}
\a{\b{If} \i{Expr} [\i{Stmt}] [\i{Stmt}]}
\a{\b{Spawn} ([(\i{Var}, \i{Type})], [\i{Stmt}]) [\i{Expr}]}
\a{\b{Assign} \i{Expr} \i{Expr}}
\a{\b{Exp} \i{Expr}}
\a{\b{Wait} \i{Expr}}
\a{\b{Exit}}
\i{Expr}
\p{\b{Call} \i{String} [\i{Expr}]}
\a{\b{Arith} \i{ArithOp} \i{Expr} \i{Expr}}
\a{\b{ArithUnop} \i{ArithUnop} \i{Expr}}
\a{\b{RelnOp} \i{RelnOp} \i{Expr} \i{Expr}}
\a{\b{Constant} \i{String}}
\a{\b{NumLit} \i{Integer}}
\a{\b{StringLit} \i{String}}
\a{\b{Var} \i{String}}
\a{\b{CurThread}}
\i{Type} 
\p{\b{Int} $\mid$ \b{Bool} $\mid$ \b{String}
   $\mid$ \b{Buffer} $\mid$ \b{Event}}
}
\caption{Front-end grammar.}
\label{fig:front-syntax}
\end{figure}

@@

\begin{figure}[ht]
\centering
\bnf{
\i{Thread}
\p{(\i{thread\_label}, [(\i{Var}, \i{Type})])}
\i{Block}
\p{(\i{label}, \i{thread\_label}, [\i{Stmt}], \i{Tail})}
\i{Tail}
\p{\b{Goto} \i{label}}
\a{\b{GotoWait} \i{label}}
\a{\b{If} \i{Expr} \i{Tail} \i{Tail}}
\a{\b{Exit}}
\i{Stmt}
\p{\b{Decl} (\i{Var}, \i{Type}) \i{Expr}}
\a{\b{Assign} \i{Expr} \i{Expr}}
\a{\b{Exp} \i{Expr}}
\a{\b{Spawn} \i{label} [((\i{Var}, \i{Type}), \i{Expr})]}
}
\caption{Back-end grammar.}
\label{fig:back-syntax}
\end{figure}

@@

In the runtime, our current thread \t{struct}s are larger than necessary.
Because the runtime allocates a \t{struct} on every thread spawn, we should
replace our \t{malloc} calls with calls to a custom slab allocator. We also plan
on writing a multithreaded runtime, to allow servicing multiple threads' ready
events simultaneously. Because our threads don't interact, this does not require
exposing any locking to the programmer.

>>>>

The underlying abstract syntax for the front-end He-Man language is a
fairly conventional imperative, block-structured, statement-based,
first-order language, shown in Figure \ref{fig:front-syntax}. The
notable constructs are \b{Spawn}, creating a new thread, which takes a
list of arguments and launches the associated code with those
arguments available to it, and \b{Wait}, which takes an event
expression as an argument and blocks until the event is
``ready''. Note that \b{Call} is for calling foreign functions; He-Man
does not have its own notion of function.

@@

\begin{figure}[ht]
\centering
\bnf{
\i{Stmt}
\p{\b{Decl} (\i{Var}, \i{Type}) \i{Expr}}
\a{\b{While} \i{Expr} [\i{Stmt}]}
\a{\b{If} \i{Expr} [\i{Stmt}] [\i{Stmt}]}
\a{\b{Spawn} ([(\i{Var}, \i{Type})], [\i{Stmt}]) [\i{Expr}]}
\a{\b{Assign} \i{Expr} \i{Expr}}
\a{\b{Exp} \i{Expr}}
\a{\b{Wait} \i{Expr}}
\a{\b{Exit}}
\i{Expr}
\p{\b{Call} \i{String} [\i{Expr}]}
\a{\b{Arith} \i{ArithOp} \i{Expr} \i{Expr}}
\a{\b{ArithUnop} \i{ArithUnop} \i{Expr}}
\a{\b{RelnOp} \i{RelnOp} \i{Expr} \i{Expr}}
\a{\b{Constant} \i{String}}
\a{\b{NumLit} \i{Integer}}
\a{\b{StringLit} \i{String}}
\a{\b{Var} \i{Var}}
\i{Type} 
\p{\b{Int} $\mid$ \b{Bool} $\mid$ \b{FD}
   $\mid$ \b{Buffer} $\mid$ \b{Event} $\mid$ $\cdots$}
}
\caption{Front-end abstract syntax.}
\label{fig:front-syntax}
\end{figure}

@@

\begin{figure}[ht]
\centering
\bnf{
\i{Thread}
\p{(\i{thread\_label}, [(\i{Var}, \i{Type})])}
\i{Block}
\p{(\i{label}, \i{thread\_label}, [\i{Stmt}], \i{Tail})}
\i{Tail}
\p{\b{Goto} \i{label}}
\a{\b{GotoWait} \i{label}}
\a{\b{If} \i{Expr} \i{Tail} \i{Tail}}
\a{\b{Exit}}
\i{Stmt}
\p{\b{Decl} (\i{Var}, \i{Type}) \i{Expr}}
\a{\b{Assign} \i{Expr} \i{Expr}}
\a{\b{Exp} \i{Expr}}
\a{\b{Spawn} \i{label} [((\i{Var}, \i{Type}), \i{Expr})]}
}
\caption{Back-end abstract syntax.}
\label{fig:back-syntax}
\end{figure}

@@

In the runtime, our current thread \t{struct}s are larger than necessary.
Because the runtime allocates a \t{struct} on every thread spawn, we should
replace our \t{malloc} calls with calls to a custom slab allocator.
